A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
wordsmithing

The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the spray schedule treatments using fungicide.  
Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments.
A a Wald-type test was used to test the impact of the disease pressure factor.

Linear contrasts were used to produce the mean difference in effect sizes, and their respective standard errors and 95% confidence intervals, between each spray schedule treatment.

Additional meta-analysis models tested variables ... for their influence on the SpraySchedule variables ability to mitigate yield loss.
For the variable disease pressure a Wald-type test was used to test the impact of this variable on the model as a whole.

>>>>

The mean difference in grain yield was estimated from the difference in model estimates of the non-treated control and each of the fungicide spray schedule treatments.
Disease pressure was tested against the basic model to determine if, when introduced as a moderator variable, it could significantly explain additional heterogeneity between the spray schedule treatments.
A a Wald-type test was used to test the impact of the disease pressure factor.

Linear contrasts were used to produce the mean difference in effect sizes and their respective standard errors and 95% confidence intervals between each spray schedule treatment.

Additional meta-analysis models tested variables ... for their influence on the SpraySchedule variables ability to mitigate yield loss.
For the variable disease pressure a Wald-type test was used to test the effect of this variable on the model as a whole.
